Repeatability Test

### 2018-05-04 pt_characterization/machine_cons_check/sodb9/res.tex
Ricks comment applied

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC1]{
		\includegraphics[scale=0.43]{sodb9/1_sec_et_hist_v5.eps}
		\label{fig:s9_inc1_et_hist_v5}
	}
	\subfigure[ET frequency on INC2]{
		\includegraphics[scale=0.43]{sodb9/2_sec_et_hist_v5.eps}
		\label{fig:s9_inc2_et_hist_v5}
	}
	\subfigure[ET frequency on INC4]{
		\includegraphics[scale=0.43]{sodb9/4_sec_et_hist_v5.eps}
		\label{fig:s9_inc4_et_hist_v5}
	}
	\subfigure[ET frequency on INC8]{
		\includegraphics[scale=0.43]{sodb9/8_sec_et_hist_v5.eps}
		\label{fig:s9_inc8_et_hist_v5}
	}
	\caption{ET Histograms of INC1 ... INC8~\label{fig:s9_et_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC16]{
		\includegraphics[scale=0.43]{sodb9/16_sec_et_hist_v5.eps}
		\label{fig:s9_inc16_et_hist_v5}
	}
	\subfigure[ET frequency on INC32]{
		\includegraphics[scale=0.43]{sodb9/32_sec_et_hist_v5.eps}
		\label{fig:s9_inc32_et_hist_v5}
	}
	\subfigure[ET frequency on INC64]{
		\includegraphics[scale=0.43]{sodb9/64_sec_et_hist_v5.eps}
		\label{fig:s9_inc64_et_hist_v5}
	}
	\subfigure[ET frequency on INC128]{
		\includegraphics[scale=0.43]{sodb9/128_sec_et_hist_v5.eps}
		\label{fig:s9_inc128_et_hist_v5}
	}
	\caption{ET Histograms of INC16 ... INC128~\label{fig:s9_et_hist2}}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC1]{
		\includegraphics[scale=0.43]{sodb9/1_sec_pt_hist_v5.eps}
		\label{fig:s9_inc1_hist_v5}
	}
	\subfigure[PT frequency on INC2]{
		\includegraphics[scale=0.43]{sodb9/2_sec_pt_hist_v5.eps}
		\label{fig:s9_inc2_hist_v5}
	}
	\subfigure[PT frequency on INC4]{
		\includegraphics[scale=0.43]{sodb9/4_sec_pt_hist_v5.eps}
		\label{fig:s9_inc4_hist_v5}
	}
	\subfigure[PT frequency on INC8]{
		\includegraphics[scale=0.43]{sodb9/8_sec_pt_hist_v5.eps}
		\label{fig:s9_inc8_hist_v5}
	}
	\caption{PT Histograms of INC1 ... INC8~\label{fig:s9_pt_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC16]{
		\includegraphics[scale=0.43]{sodb9/16_sec_pt_hist_v5.eps}
		\label{fig:s9_inc16_hist_v5}
	}
	\subfigure[PT frequency on INC32]{
		\includegraphics[scale=0.43]{sodb9/32_sec_pt_hist_v5.eps}
		\label{fig:s9_inc32_hist_v5}
	}
	\subfigure[PT frequency on INC64]{
		\includegraphics[scale=0.43]{sodb9/64_sec_pt_hist_v5.eps}
		\label{fig:s9_inc64_hist_v5}
	}
	\subfigure[PT frequency on INC128]{
		\includegraphics[scale=0.43]{sodb9/128_sec_pt_hist_v5.eps}
		\label{fig:s9_inc128_hist_v5}
	}
	\caption{PT Histograms of INC16 ... INC64~\label{fig:s9_pt_hist2}}
\end{figure}

>>>>

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC1 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/1_sec_et_hist_v5.eps}
		\label{fig:s9_inc1_et_hist_v5}
	}
	\subfigure[ET frequency on INC2 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/2_sec_et_hist_v5.eps}
		\label{fig:s9_inc2_et_hist_v5}
	}
	\subfigure[ET frequency on INC4 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/4_sec_et_hist_v5.eps}
		\label{fig:s9_inc4_et_hist_v5}
	}
	\subfigure[ET frequency on INC8 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/8_sec_et_hist_v5.eps}
		\label{fig:s9_inc8_et_hist_v5}
	}
	\caption{ET Histograms of INC1 ... INC8~\label{fig:s9_et_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC16 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/16_sec_et_hist_v5.eps}
		\label{fig:s9_inc16_et_hist_v5}
	}
	\subfigure[ET frequency on INC32 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/32_sec_et_hist_v5.eps}
		\label{fig:s9_inc32_et_hist_v5}
	}
	\subfigure[ET frequency on INC64 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/64_sec_et_hist_v5.eps}
		\label{fig:s9_inc64_et_hist_v5}
	}
	\subfigure[ET frequency on INC128 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/128_sec_et_hist_v5.eps}
		\label{fig:s9_inc128_et_hist_v5}
	}
	\caption{ET Histograms of INC16 ... INC128~\label{fig:s9_et_hist2}}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC1 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/1_sec_pt_hist_v5.eps}
		\label{fig:s9_inc1_hist_v5}
	}
	\subfigure[PT frequency on INC2 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/2_sec_pt_hist_v5.eps}
		\label{fig:s9_inc2_hist_v5}
	}
	\subfigure[PT frequency on INC4 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/4_sec_pt_hist_v5.eps}
		\label{fig:s9_inc4_hist_v5}
	}
	\subfigure[PT frequency on INC8 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/8_sec_pt_hist_v5.eps}
		\label{fig:s9_inc8_hist_v5}
	}
	\caption{PT Histograms of INC1 ... INC8~\label{fig:s9_pt_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC16 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/16_sec_pt_hist_v5.eps}
		\label{fig:s9_inc16_hist_v5}
	}
	\subfigure[PT frequency on INC32 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/32_sec_pt_hist_v5.eps}
		\label{fig:s9_inc32_hist_v5}
	}
	\subfigure[PT frequency on INC64 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/64_sec_pt_hist_v5.eps}
		\label{fig:s9_inc64_hist_v5}
	}
	\subfigure[PT frequency on INC128 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{sodb9/128_sec_pt_hist_v5.eps}
		\label{fig:s9_inc128_hist_v5}
	}
	\caption{PT Histograms of INC16 ... INC64~\label{fig:s9_pt_hist2}}
\end{figure}

### 2018-05-04 pt_characterization/real_data/paper.tex
realistic programs
Ricks comment applied

@@

@@

\subsection{Insertion Sort on {\tt sodb9}~\label{sec:new_ins_sort}} 
This section shows a series of histograms of an insertion sorting program that 
sorts the elements of a given array in non-decreasing order. 
The program repeatedly runs 300 times for a given input size. 
Note that each sort program over a specific input size is termed SORT{\it x}: 
for instance, SORT100 indicates the insertion sort program over 100K elements. 
(This experiment was performed on {\tt sodb9}.)

@@

\subsection{One-to-One Comparison between An Insertion Sort \& A Corresponding INC Programs~\label{sec:sort}} 
This section compares program time histograms 
of an insertion sort and a nested-for-loop programs (termed INC) with different input sizes. The insertion sort program sorts the elements of a given array in non-decreasing order.  The program repeatedly runs 300 times for a given input size. The input size for the program varies from 144K to 344K integer elements, which are randomly generated. Note that each sort program over a specific input size is termed SORT{\it x}: for instance, SORT100 indicates the insertion sort program over 100K elements. An INC program's task length is correspondingly determined by the program time of an SORT program. In Figures~\ref{fig:sort1},~\ref{fig:sort2}, and~\ref{fig:sort3} 
we perform a match on an SORT program and its corresponding INC program.

@@

\subsection{Insertion Sort on {\tt sodb8}~\label{sec:add_new}} 
This section shows a series of histograms of an insertion sorting program that 
sorts the elements of a given array in non-decreasing order. 
The program repeatedly runs 300 times for a given input size. 
The input size for the program 
varies from 100,000 to 1,160,000 integer elements, which are randomly generated. 
Note that each sort program over a specific input size is termed SORT{\it x}: 
for instance, SORT100 indicates the insertion sort program over 100K elements. 
This experiment was performed on {\tt sodb8}.

@@

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in column major 
as the input sizes grows. The program was run on {\tt sodb10}.

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in row major as the input sizes grows. 
The program was run on {\tt sodb12}.

>>>>

%\clearpage
%\pagebreak

\paragraph{Experimental Notes:} In the experiments 
we also used four nodes ({\tt sodb8}, {\tt sodb9}, {\tt sodb10}, and {\tt sodb12} ) in the same cluster. 
A short summary of the experiments is shown in Table~\ref{tab:exp_notes}.

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
%{\tt sodb8}  (plugged into {\em bottom left} power strip) & SORT100, SORT200, SORT400, SORT800 & Runs of 300 samples & 2018-??-?? $\sim$2018-??-??\\ \hline
{\tt sodb9}  (plugged into {\em the upper left} power strip) & SORT100, SORT200, SORT400, SORT800 & Runs of 300 samples & 2018-04-09 $\sim$2018-04-12\\ \hline
{\tt sodb10} (plugged into {\em the upper left} power strip)  & MATC1K, MATC2K, MATC4K, MATC8K & Runs of 300 samples & 2018-03-02 $\sim$2018-03-12 \\ \hline
{\tt sodb12} (plugged into {\em the upper left} power strip) & MATR1K, MATR2K, MATR4K, MATR8K& Runs of 300 samples & 2018-03-02 $\sim$2018-03-12 \\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes}}
\end{table}

@@

\subsection{Insertion Sort on {\tt sodb9}~\label{sec:new_ins_sort}} 
This section shows a series of histograms of an insertion sorting program that 
sorts the elements of a given array in non-decreasing order. 
The program repeatedly runs 300 times for a given input size. 
Note that each sort program over a specific input size is termed SORT{\it x}: 
for instance, SORT100 indicates the insertion sort program over 100K elements. 
This experiment was performed on {\tt sodb9} plugged into {\em the upper left} power strip.

@@

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in column major 
as the input sizes grows. The program was run on {\tt sodb10} plugged into {\em the upper left} power strip.

Figure~\ref{fig:matc} shows a series of 
histograms of the execution times measured on 
the same matrix multiplication program in row major as the input sizes grows. 
The program was run on {\tt sodb12} plugged into {\em the upper left} power strip.

@@

\subsection{Insertion Sort on {\tt sodb8}~\label{sec:add_new}} 
This section shows a series of histograms of an insertion sorting program that 
sorts the elements of a given array in non-decreasing order. 
The program repeatedly runs 300 times for a given input size. 
The input size for the program 
varies from 100,000 to 1,160,000 integer elements, which are randomly generated. 
Note that each sort program over a specific input size is termed SORT{\it x}: 
for instance, SORT100 indicates the insertion sort program over 100K elements. 
This experiment was performed on {\tt sodb8} plugged into {\em bottom left} power strip.

\subsection{One-to-One Comparison between An Insertion Sort \& A Corresponding INC Programs~\label{sec:sort}} 
This section compares program time histograms 
of an insertion sort and a nested-for-loop programs (termed INC) with different input sizes. The insertion sort program sorts the elements of a given array in non-decreasing order.  The program repeatedly runs 300 times for a given input size. The input size for the program varies from 144K to 344K integer elements, which are randomly generated. Note that each sort program over a specific input size is termed SORT{\it x}: for instance, SORT100 indicates the insertion sort program over 100K elements. An INC program's task length is correspondingly determined by the program time of an SORT program. In Figures~\ref{fig:sort1},~\ref{fig:sort2}, and~\ref{fig:sort3} 
we perform a match on an SORT program and its corresponding INC program. 
{\tt sodb8} was plugged into {\em bottom left} power strip 
while {\tt sodb10} plugged into {\em the upper left} power strip.

@@

@@

### 2018-05-04 pt_characterization/rep_check/1024_run.tex
Ricks comment applied

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{3cm}|p{4cm}|p{3.5cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} &  INC1024 & 300 samples, each & 2017-04-12 $\sim$ 2017-04-23 & 
Figs.~\ref{fig:s9_inc1024_et} and~\ref{fig:s9_inc1024_pt}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:inc1024_run_notes}}
\end{table}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC1024-Run1]{
		\includegraphics[scale=0.28]{1024_run/1024_sec_et_hist1.eps}
		\label{fig:inc1024_run1_et}
	}
	\subfigure[ET frequency on INC1024-Run2]{
		\includegraphics[scale=0.28]{1024_run/1024_sec_et_hist2.eps}
		\label{fig:inc1024_run2_et}
	}
	\subfigure[ET frequency on INC1024-Run3]{
		\includegraphics[scale=0.28]{1024_run/1024_sec_et_hist3.eps}
		\label{fig:inc1024_run3_et}
	}
	\caption{ET Histograms of Three Consecutive INC1024 Runs\label{fig:s9_inc1024_et}}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC1024-Run1]{
		\includegraphics[scale=0.28]{1024_run/1024_sec_pt_hist1.eps}
		\label{fig:inc1024_run1_pt}
	}
	\subfigure[PT frequency on INC1024-Run2]{
		\includegraphics[scale=0.28]{1024_run/1024_sec_pt_hist2.eps}
		\label{fig:inc1024_run2_pt}
	}
	\subfigure[PT frequency on INC1024-Run3]{
		\includegraphics[scale=0.28]{1024_run/1024_sec_pt_hist3.eps}
		\label{fig:inc1024_run3_pt}
	}
	\caption{PT Histograms of Three Consecutive INC1024 Runs\label{fig:s9_inc1024_pt}}
\end{figure}

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{3cm}|p{4cm}|p{3.5cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} (plugged into {\em the upper left} power strip) &  INC1024 & 300 samples, each & 2017-04-12 $\sim$ 2017-04-23 & 
Figs.~\ref{fig:s9_inc1024_et} and~\ref{fig:s9_inc1024_pt}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:inc1024_run_notes}}
\end{table}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC1024-Run1 on {\tt sodb9}]{
		\includegraphics[scale=0.28]{1024_run/1024_sec_et_hist1.eps}
		\label{fig:inc1024_run1_et}
	}
	\subfigure[ET frequency on INC1024-Run2 on {\tt sodb9}]{
		\includegraphics[scale=0.28]{1024_run/1024_sec_et_hist2.eps}
		\label{fig:inc1024_run2_et}
	}
	\subfigure[ET frequency on INC1024-Run3 on {\tt sodb9}]{
		\includegraphics[scale=0.28]{1024_run/1024_sec_et_hist3.eps}
		\label{fig:inc1024_run3_et}
	}
	\caption{ET Histograms of Three Consecutive INC1024 Runs\label{fig:s9_inc1024_et}}
\end{figure}

\clearpage
\newpage

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC1024-Run1 on {\tt sodb9}]{
		\includegraphics[scale=0.28]{1024_run/1024_sec_pt_hist1.eps}
		\label{fig:inc1024_run1_pt}
	}
	\subfigure[PT frequency on INC1024-Run2 on {\tt sodb9}]{
		\includegraphics[scale=0.28]{1024_run/1024_sec_pt_hist2.eps}
		\label{fig:inc1024_run2_pt}
	}
	\subfigure[PT frequency on INC1024-Run3 on {\tt sodb9}]{
		\includegraphics[scale=0.28]{1024_run/1024_sec_pt_hist3.eps}
		\label{fig:inc1024_run3_pt}
	}
	\caption{PT Histograms of Three Consecutive INC1024 Runs\label{fig:s9_inc1024_pt}}
\end{figure}

### 2018-05-04 pt_characterization/rep_check/10k_run.tex
Ricks comment applied

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{3cm}|p{4cm}|p{3.5cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} &  INC8 & 10000 samples & 2017-03-29 $\sim$ 2017-03-30 & Figs.~\ref{fig:inc8_10k_et_hist_v5} and~\ref{fig:inc8_10k_pt_hist_v5}\\ \hline
{\tt sodb10} &  INC16 & 10000 samples & 2017-03-29 $\sim$ 2017-03-31 & 
Figs.~\ref{fig:inc16_10k_et_hist_v5} and~\ref{fig:inc16_10k_pt_hist_v5}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes3}}
\end{table}

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC8]{
		\includegraphics[scale=0.43]{10k_run/8_sec_et_hist_v5.eps}
		\label{fig:inc8_10k_et_hist_v5}
	}
	\subfigure[PT frequency on INC8]{
		\includegraphics[scale=0.43]{10k_run/8_sec_pt_hist_v5.eps}
		\label{fig:inc8_10k_pt_hist_v5}
	}
	\subfigure[ET frequency on INC16]{
		\includegraphics[scale=0.43]{10k_run/16_sec_et_hist_v5.eps}
		\label{fig:inc16_10k_et_hist_v5}
	}
	\subfigure[PT frequency on INC16]{
		\includegraphics[scale=0.43]{10k_run/16_sec_pt_hist_v5.eps}
		\label{fig:inc16_10k_pt_hist_v5}
	}
	\caption{Histograms of INC8 and INC16 with 10,000 samples~\label{fig:10k_run_hist}}
\end{figure}

>>>>

\begin{table}[h]
\begin{center}
\begin{tabular}{|p{2cm}|p{3cm}|p{3cm}|p{4cm}|p{3.5cm}|} \hline
Machine & Task Length (sec) & Description & Experiment Period & Relevant \linebreak Histograms\\ \hline
{\tt sodb9} (plugged into {\em the upper left} power strip) &  INC8 & 10,000 samples & 2017-03-29 $\sim$ 2017-03-30 & Figs.~\ref{fig:inc8_10k_et_hist_v5} and~\ref{fig:inc8_10k_pt_hist_v5}\\ \hline
{\tt sodb10} (plugged into {\em the upper left} power strip) &  INC16 & 10,000 samples & 2017-03-29 $\sim$ 2017-03-31 & 
Figs.~\ref{fig:inc16_10k_et_hist_v5} and~\ref{fig:inc16_10k_pt_hist_v5}\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Notes on experiment runs used for histograms\label{tab:exp_notes3}}
\end{table}

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC8 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{10k_run/8_sec_et_hist_v5.eps}
		\label{fig:inc8_10k_et_hist_v5}
	}
	\subfigure[PT frequency on INC8 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{10k_run/8_sec_pt_hist_v5.eps}
		\label{fig:inc8_10k_pt_hist_v5}
	}
	\subfigure[ET frequency on INC16 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{10k_run/16_sec_et_hist_v5.eps}
		\label{fig:inc16_10k_et_hist_v5}
	}
	\subfigure[PT frequency on INC16 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{10k_run/16_sec_pt_hist_v5.eps}
		\label{fig:inc16_10k_pt_hist_v5}
	}
	\caption{Histograms of INC8 and INC16 with 10,000 samples~\label{fig:10k_run_hist}}
\end{figure}
